Dependent Object Types

### 2012-08-08 article.tex
paths p not v
- to \emptyset for clarity

Two subclasses of terms are values $v$, which consist of just
variables, and paths $v$ which consist of just variables and field
selections.

@@

\subsection{Type Safety}
Type-safety states that a well-typed program doesn't get stuck. More
formally: If $- \ts t \typ T$ and $\reductionl t - {t'} {s'} *$ then
either $t'$ is a value or $\exists t'', s'', \reduction {t'} {s'}
{t''} {s''}$.

@@

$\Gamma \ds t : T$ is simply defined as $t \in \rele k \Gamma - T,
\forall k$.

@@

\begin{myproof}
The proof is on induction on the derivation of $\Gamma \ts t : T$. For
each case, we need to show $t \in \rele k \Gamma - T, \forall k$. The
non-trivial case is to need to show ${t'} \in \relv {k-j-1} {\Gamma'}
{s'} T$ by supposing $k > 0$, $s \in \rels k \Gamma -$, and, for some
$j \leq k$, $\reductionl {t} s {t'} {s'} j \andl \irred {t'}
{s'} \andl \Gamma' \in \relg \Gamma k {s'} \Gamma$.

@@

%Need to show $t_1.l_i \in \rele k \Gamma - T$. Suppose $k > 0$ and $s
%\in \rels k \Gamma -$. Suppose, for some $j \leq k$, $\reductionl
%    {t_1.l_i} s {t'} {s'} j \andl \irred {t'} {s'} \andl \Gamma' \in
%    \relg \Gamma k {s'} \Gamma$. Remains to show ${t'} \in \relv
%          {k-j-1} {\Gamma'} {s'} T$.

@@

%Need to show $t_1.m_i(t_2) \in \rele k \Gamma - T$. Suppose $k > 0$
%and $s \in \rels k \Gamma -$. Suppose, for some $j \leq k$,
%$\reductionl {t_1.m_i(t_2)} s {t'} {s'} j \andl \irred {t'} {s'} \andl
%\Gamma' \in \relg \Gamma k {s'} \Gamma$. Remains to show ${t'} \in
%\relv {k-j-1} {\Gamma'} {s'} T$.

@@

%Need to show $\new y c {t'} \in \rele k \Gamma - T$. Suppose $k > 0$
%and $s \in \rels k \Gamma -$. Suppose, for some $j \leq k$,
%$\reductionl {\new y c {t'}} s {t''} {s''} j \andl \irred {t''} {s''} \andl
%\Gamma'' \in \relg \Gamma k {s''} \Gamma$. Remains to show ${t''} \in
%\relv {k-j-1} {\Gamma''} {s''} T$.

>>>>

Two subclasses of terms are values $v$, which consist of just
variables, and paths $p$ which consist of just variables and field
selections.

@@

\subsection{Type Safety}
Type-safety states that a well-typed program doesn't get stuck. More
formally: If $\emptyset \ts t \typ T$ and $\reductionl t \emptyset {t'} {s'} *$ then
either $t'$ is a value or $\exists t'', s'', \reduction {t'} {s'}
{t''} {s''}$.

@@

$\Gamma \ds t : T$ is simply defined as $t \in \rele k \Gamma \emptyset T,
\forall k$.

@@

\begin{myproof}
The proof is on induction on the derivation of $\Gamma \ts t : T$. For
each case, we need to show $t \in \rele k \Gamma \emptyset T, \forall k$. The
non-trivial case is to need to show ${t'} \in \relv {k-j-1} {\Gamma'}
{s'} T$ by supposing $k > 0$, $s \in \rels k \Gamma \emptyset$, and, for some
$j \leq k$, $\reductionl {t} s {t'} {s'} j \andl \irred {t'}
{s'} \andl \Gamma' \in \relg \Gamma k {s'} \Gamma$.

@@

%Need to show $t_1.l_i \in \rele k \Gamma \emptyset T$. Suppose $k > 0$ and $s
%\in \rels k \Gamma \emptyset$. Suppose, for some $j \leq k$, $\reductionl
%    {t_1.l_i} s {t'} {s'} j \andl \irred {t'} {s'} \andl \Gamma' \in
%    \relg \Gamma k {s'} \Gamma$. Remains to show ${t'} \in \relv
%          {k-j-1} {\Gamma'} {s'} T$.

@@

%Need to show $t_1.m_i(t_2) \in \rele k \Gamma \emptyset T$. Suppose $k > 0$
%and $s \in \rels k \Gamma \emptyset$. Suppose, for some $j \leq k$,
%$\reductionl {t_1.m_i(t_2)} s {t'} {s'} j \andl \irred {t'} {s'} \andl
%\Gamma' \in \relg \Gamma k {s'} \Gamma$. Remains to show ${t'} \in
%\relv {k-j-1} {\Gamma'} {s'} T$.

@@

%Need to show $\new y c {t'} \in \rele k \Gamma \emptyset T$. Suppose $k > 0$
%and $s \in \rels k \Gamma \emptyset$. Suppose, for some $j \leq k$,
%$\reductionl {\new y c {t'}} s {t''} {s''} j \andl \irred {t''} {s''} \andl
%\Gamma'' \in \relg \Gamma k {s''} \Gamma$. Remains to show ${t''} \in
%\relv {k-j-1} {\Gamma''} {s''} T$.
